---
title             : "Reproducing the analysis of Schroeder and Epley (2015)"
shorttitle        : "The Sound of Intellect"

author: 
  - name          : "Soyeon Lee"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "2900 Bedford Ave"
    email         : "soyeon.lee28@bcmail.cuny.edu"
    
affiliation:
  - id            : "1"
    institution   : "Brooklyn College of the City University of New York"
 
authornote: |
  Soyeon Lee, Experimental Psychology Student, Broklyn College of the City of New York.

abstract: |
  A reproduction of the analysis for Experiment 4 from Schroeder and Epley (2015). 
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "Voice, Intellect"
wordcount         : "X"

bibliography      : ["r-references.bib","myreferences.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```
# Introduction

This report reproduces the analysis of Experiment 4 reported in @schroeder_sound_2015. The citation for the article is:
  
Schroeder, J., & Epley, N. (2015). The sound of intellect: Speech reveals a thoughtful mind, increasing a job candidate’s appeal. Psychological science, 26(6), 877-891.

The data were downloaded from https://raw.githubusercontent.com/CrumpLab/statisticsLab/master/data/SchroederEpley2015data.csv

@schroeder_sound_2015 investigated perception of intellect inferred from speech involved in hiring process. In Experiment 4, the professional recruiters rated hypothetical candidates' intellect, impression, and hiring likeliness based on pitches delivered via audio or transcript. This report replicates the authors' analysis of the effects of two conditions (audio vs. transcript) on the impression and hire rating using independent samples t tests.

# Methods

## Participants

There were 39 professional recruiters from Fortune 500 companies.

## Material

Three randomly selected candidate pitches from Experiment 1 were used.

## Procedure

The experiment was conducted online. Randomly assigned recruiters either read or listened to candidates' pitches. The recruiters' responses on intellect, impression and hire ratings of candidates were recorded.

# Results
```{r,echo=FALSE,warning=FALSE,message=FALSE}
#load libraries and data
library(papaja)
library(dplyr)
library(ggplot2)
library(tidyverse)

all_data<-read.csv("SchroederEpley2015data.csv", header=TRUE)
all_data<-all_data%>% rename(condition=ï..CONDITION)
```
For each dimension (impression and hire), mean rating scores for each condition (transcript and voice) were submitted to independent samples t tests. Means and standard deviations in each condition for Impression ratings dimension are displayed in Table 1, and Figure 1.  Means and standard deviations in each condition for Hire ratings dimension are displayed in Table 2, and Figure 1.

```{r,warning=FALSE, message=FALSE}
#t tests for impression and hire rating
all_data$condition <- as.factor(all_data$condition)
levels(all_data$condition) <- c("transcript","audio")

impression_results<-t.test(all_data[all_data$condition=='audio',]$Impression_Rating,
                           all_data[all_data$condition=='transcript',]$Impression_Rating,
                           var.equal=TRUE)

hire_results<-t.test(all_data[all_data$condition=='audio',]$Hire_Rating,
                     all_data[all_data$condition=='transcript',]$Hire_Rating,
                     var.equal=TRUE)

##Make and print the tables
impression_samples<-all_data%>%group_by(condition)%>%
  summarize(Mean=mean(Impression_Rating),
            SD=sd(Impression_Rating)
            )
impression_samples[,-1]<-printnum(impression_samples[,-1])

apa_table(
  impression_samples,
    caption="Impression Rating samples.",
    escape=TRUE
)

hire_samples<-all_data%>%group_by(condition)%>%
  summarize(Mean=mean(Hire_Rating),
            SD=sd(Hire_Rating)
            )
hire_samples[,-1]<-printnum(hire_samples[,-1])

apa_table(
  hire_samples,
    caption="Hire Rating samples.",
    escape=TRUE
)
```

```{r,warning=FALSE, message=FALSE}
#Make and print figures
CONDITION <- rep(all_data$condition,3)

ratings<-c(all_data$Intellect_Rating,
           all_data$Impression_Rating,
           all_data$Hire_Rating)

num_to_repeat<-length(all_data$condition)

rating_type<-rep(c("Intellect","General Impression","Hiring Likelihood"),num_to_repeat)

plot_all<-data.frame(CONDITION,rating_type,ratings)

descriptive_all<-plot_all %>%
                  group_by(CONDITION,rating_type)%>%
                  summarise(means=mean(ratings),
                            SEs=sd(ratings)/sqrt(length(ratings)))

apa_barplot(descriptive_all,
        aes(x=rating_type, y=means, group=CONDITION))+
    geom_bar(stat="identity",aes(fill=CONDITION),position="dodge")+
        ylab("Recruiters' Evaluation of Candidates")+
        theme_classic()+
    geom_errorbar(aes(ymin=means-SEs,
                      ymax=means+SEs),
                  width=.25,
                  position=position_dodge(width = .9))
```


# Discussion


\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
