---
title: "Reprod report draft"
author: "Soyeon Lee"
date: "12/18/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Introduction

This report reproduces two analyses in Experiment 4 by Schroder and Epley (2015). The citation for the article is:
  
Schroeder, J., & Epley, N. (2015). The sound of intellect: Speech reveals a thoughtful mind, increasing a job candidate’s appeal. Psychological science, 26(6), 877-891.

The data were downloaded from https://raw.githubusercontent.com/CrumpLab/statisticsLab/master/data/SchroederEpley2015data.csv

To study the perception of intellect inferred from speech, Schroeder and Epley (2015) investigated completed four experiments. In Experiment 4, the professional recruiters rated the candidates' intellect, impression, and hiring likelihood based on pitches delivered via audio or transcript. This report replicates two analyses: the effects of two conditions (audio vs. transcript) on impression and hire rating, using independent samples t tests.


##Re-analysis
```{r}
library(papaja)
library(dplyr)
library(ggplot2)
library(tidyverse)

#load data
all_data<-read.csv("SchroederEpley2015data.csv", header=TRUE)
all_data<-all_data%>% rename(condition=ï..CONDITION)

all_data$condition <- as.factor(all_data$condition)
levels(all_data$condition) <- c("transcript","audio")

impression_results<-t.test(all_data[all_data$condition=='audio',]$Impression_Rating,
                           all_data[all_data$condition=='transcript',]$Impression_Rating,
                           var.equal=TRUE)

hire_results<-t.test(all_data[all_data$condition=='audio',]$Hire_Rating,
                     all_data[all_data$condition=='transcript',]$Hire_Rating,
                     var.equal=TRUE)
```

###tables of means for each condition
```{r}
library(dplyr)
impression_samples<-all_data%>%group_by(condition)%>%
  summarize(Mean=mean(Impression_Rating),
            SD=sd(Impression_Rating)
            )
impression_samples[,-1]<-printnum(impression_samples[,-1])

apa_table(
  impression_samples,
    caption="Impression Rating samples.",
    escape=TRUE
)

hire_samples<-all_data%>%group_by(condition)%>%
  summarize(Mean=mean(Hire_Rating),
            SD=sd(Hire_Rating)
            )
hire_samples[,-1]<-printnum(hire_samples[,-1])

apa_table(
  hire_samples,
    caption="Hire Rating samples.",
    escape=TRUE
)


```