---
title: "ReproducibleReport"
author: "Soyeon Lee"
date: "12/18/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Introduction

This report reproduces the analysis of Experiment 4 reported in Schroder and Epley (2015). The citation for the article is:
  
Schroeder, J., & Epley, N. (2015). The sound of intellect: Speech reveals a thoughtful mind, increasing a job candidate’s appeal. Psychological science, 26(6), 877-891.

The data were downloaded from https://raw.githubusercontent.com/CrumpLab/statisticsLab/master/data/SchroederEpley2015data.csv

Schroeder and Epley (2015) investigated perception of intellect inferred from speech involved in hiring process. In Experiment 4, the professional recruiters rated candidates' intellect, impression, and hiring likeliness based on pitches delivered via audio or transcript. This report replicates the authors' analysis of the effects of two conditions (audio vs. transcript) on the impression and hire rating using independent samples t tests.


##Re-analysis
```{r,echo=FALSE,warning=FALSE,message=FALSE}
#load libraries and data
library(papaja)
library(dplyr)
library(ggplot2)
library(tidyverse)

all_data<-read.csv("SchroederEpley2015data.csv", header=TRUE)
all_data<-all_data%>% rename(condition=ï..CONDITION)

#t tests for impression and hire rating
all_data$condition <- as.factor(all_data$condition)
levels(all_data$condition) <- c("transcript","audio")

impression_results<-t.test(all_data[all_data$condition=='audio',]$Impression_Rating,
                           all_data[all_data$condition=='transcript',]$Impression_Rating,
                           var.equal=TRUE)

hire_results<-t.test(all_data[all_data$condition=='audio',]$Hire_Rating,
                     all_data[all_data$condition=='transcript',]$Hire_Rating,
                     var.equal=TRUE)
```

###tables of means for each condition
```{r}
impression_samples<-all_data%>%group_by(condition)%>%
  summarize(Mean=mean(Impression_Rating),
            SD=sd(Impression_Rating)
            )
impression_samples[,-1]<-printnum(impression_samples[,-1])

apa_table(
  impression_samples,
    caption="Impression Rating samples.",
    escape=TRUE
)

hire_samples<-all_data%>%group_by(condition)%>%
  summarize(Mean=mean(Hire_Rating),
            SD=sd(Hire_Rating)
            )
hire_samples[,-1]<-printnum(hire_samples[,-1])

apa_table(
  hire_samples,
    caption="Hire Rating samples.",
    escape=TRUE
)
```

###Reproducing the figure
```{r}
CONDITION <- rep(all_data$condition,3)

ratings<-c(all_data$Intellect_Rating,
           all_data$Impression_Rating,
           all_data$Hire_Rating)

num_to_repeat<-length(all_data$condition)

rating_type<-rep(c("Intellect","General Impression","Hiring Likelihood"),num_to_repeat)

plot_all<-data.frame(CONDITION,rating_type,ratings)

descriptive_all<-plot_all %>%
                  group_by(CONDITION,rating_type)%>%
                  summarise(means=mean(ratings),
                            SEs=sd(ratings)/sqrt(length(ratings)))

ggplot(descriptive_all,
        aes(x=rating_type, y=means, group=CONDITION))+
    geom_bar(stat="identity",aes(fill=CONDITION),position="dodge")+
        ylab("Recruiters' Evaluation of Candidates")+
        theme_classic()+
    geom_errorbar(aes(ymin=means-SEs,
                      ymax=means+SEs),
                  width=.25,
                  position=position_dodge(width = .9))
```


##Results

The professional recruiters formed more positive impressions from listening to candidates' pitches than reading them in a script,`r apa_print(impression_results)$full_result`. The same pattern of evaluations was found in the hiring likeliness dimension. The preference to hire a candidate was higher when recruiters listened to pitches, rather than reading them in script,`r apa_print(hire_results)$full_result`. 


##Discussion

In Experiment 4, the authors replicated previous experiments to investigate the real-world application. In Experiments 1-3, hypothetical employers judged that the candidates are more competent, thoughtful, and intelligent when they heard candidates' pitches rather than reading them. In addition, hearing pitches resulted in a more positive impression and increased willingness to hire the candidate. Experiment 4 revealed the same pattern of evaluation.  The use of professional recruiters in Experiment 4 provided the ecological validity of the finding. 

The re-analysis successfully reproduced the analysis reported by Schroederand Epley (2015). One issue experienced in this replication is the order of conditions (audio vs. transcript) in the replicated figure. In the earlier code chunks, I put them in reverse to obtain a positive t statistic for results.  This seemingly resulted in switching the orders in the replicated figure. The bar for transcript level is on the left of the audio level for each dimension.
