---
title: "ReproducibleReport"
author: "Soyeon Lee"
date: "12/18/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Introduction

This report reproduces the analysis of Experiment 4 reported in Schroder and Epley (2015). The citation for the article is:
  
Schroeder, J., & Epley, N. (2015). The sound of intellect: Speech reveals a thoughtful mind, increasing a job candidate’s appeal. Psychological science, 26(6), 877-891.

The data were downloaded from https://raw.githubusercontent.com/CrumpLab/statisticsLab/master/data/SchroederEpley2015data.csv

Schroeder and Epley (2015) investigated perception of intellect inferred from speech involved in hiring process. In Experiment 4, the professional recruiters rated candidates' intellect, impression, and hiring likeliness based on pitches delivered via audio or transcript. This report replicates the authors' analysis of the effects of two conditions (audio vs. transcript) on impression and hire rating scores using independent samples t tests.


##Re-analysis
```{r,echo=FALSE,warning=FALSE,message=FALSE}
#load libraries and data
library(papaja)
library(dplyr)
library(ggplot2)
library(tidyverse)

all_data<-read.csv("SchroederEpley2015data.csv", header=TRUE)
all_data<-all_data%>% rename(condition=ï..CONDITION)

#t tests for impression and hire rating
all_data$condition <- as.factor(all_data$condition)
levels(all_data$condition) <- c("transcript","audio")

impression_results<-t.test(all_data[all_data$condition=='audio',]$Impression_Rating,
                           all_data[all_data$condition=='transcript',]$Impression_Rating,
                           var.equal=TRUE)

hire_results<-t.test(all_data[all_data$condition=='audio',]$Hire_Rating,
                     all_data[all_data$condition=='transcript',]$Hire_Rating,
                     var.equal=TRUE)
```

###tables of means for each condition
```{r,warning=FALSE, message=FALSE}
impression_samples<-all_data%>%group_by(condition)%>%
  summarize(Mean=mean(Impression_Rating),
            SD=sd(Impression_Rating)
            )
impression_samples[,-1]<-printnum(impression_samples[,-1])

apa_table(
  impression_samples,
    caption="Impression Rating samples.",
    escape=TRUE
)

hire_samples<-all_data%>%group_by(condition)%>%
  summarize(Mean=mean(Hire_Rating),
            SD=sd(Hire_Rating)
            )
hire_samples[,-1]<-printnum(hire_samples[,-1])

apa_table(
  hire_samples,
    caption="Hire Rating samples.",
    escape=TRUE
)
```

###Reproducing the figure
```{r,warning=FALSE, message=FALSE}
#Make and print figures 
impression_plot<-all_data%>%group_by(condition)%>%
  summarize(Impression_Mean=mean(Impression_Rating),
            Impression_SEs=sd(Impression_Rating)/
                           sqrt(length(Impression_Rating)))
            
impression_barplot<-data.frame(impression_plot)

ggplot(impression_barplot,aes(x=condition,
                              y=Impression_Mean,
                              fill=condition))+
  geom_col(position='dodge')+
  geom_errorbar(aes(ymin=Impression_Mean-Impression_SEs,
                    ymax=Impression_Mean+Impression_SEs),
                width=.2,
                position=position_dodge(width=.9))+
  theme_apa(box=TRUE)+
  labs(x="Conditions",
       y="Recruiters' Evaluatons of Candidates",
       title="Figure 1. Impression Ratings")+
  scale_fill_grey()
  

hire_plot<-all_data%>%group_by(condition)%>%
  summarize(Hire_Mean=mean(Hire_Rating),
            Hire_SEs=sd(Hire_Rating)/
                           sqrt(length(Hire_Rating)))
   
hire_barplot<-data.frame(hire_plot)

ggplot(hire_barplot,aes(x=condition,
                        y=Hire_Mean,
                        fill=condition))+
  geom_col(position='dodge')+
  geom_errorbar(aes(ymin=Hire_Mean-Hire_SEs,
                    ymax=Hire_Mean+Hire_SEs),
                width=.2,
                position=position_dodge(width=.9))+
  theme_apa(box=TRUE)+
  labs(x="Conditions",
       y="Recruiters' Evaluatons of Candidates",
       title="Figure 2. Hire Ratings")+
  scale_fill_grey()
```
##Results
The professional recruiters formed more positive impressions from listening to candidates' pitches(M=5.97,SD=1.92) than reading them in a script(M=4.07,SD=2.23),t(37)=2.85, p=.007, mean difference=1.89, 95% CI [0.55,3.24]. Similarly, recruiters were more likely to hire a candidate when recruiters listened to his or pitches (M=4.71,SD=2.26), rather than reading them in script (M=2.89,SD=2.06),t(37)=2.62,p=.013, mean difference=1.83, 95%CI [0.41,3.24]. 

##Discussion
The re-analysis successfully reproduced the analysis reported by Schroeder and Epley (2015), with a minor difference from the original analysis.  For p-value report in Hire rating, Schroeder and Epley (2015) reported p<.01.  The exact p-value obtained in this re-analysis was p=.013. 

